Measuring the Price of Anarchy in Critical Care Unit Interactions

### 2014-12-09 Paper/paper.tex
Clarifying use of pure strategies

This game is equivalent to a bi matrix game with restriction to pure strategies where both players aim to get their utilisation as close as possible to a certain target.
As such a Nash Equilibrium is not guaranteed by traditional game theoretical results \cite{Nash1950}, but based on discussions with ABUHB, long term threshold policies are a realistic consideration.

>>>>

This game is equivalent to a bi matrix game with restriction to pure strategies where both players aim to get their utilisation as close as possible to a certain target.
As such a Nash Equilibrium is not guaranteed by traditional game theoretical results \cite{Nash1950}, which guarantee the existence of equilibria in mixed strategies.
Based on discussions with ABUHB, long term threshold policies are a realistic consideration and so a pure strategy space is used.
